On the adhesivity of EGGS

### 2025-02-23 calco/main.tex
qualche pezzo di intro

>>>>

\begin{itemize}
\item general on adhesive categories
\item general on the use of eggs
\end{itemize}

In the original definition, e-graphs are defined as term graphs with an additional notion of equivalence on nodes. 
Adopting the more modern presentation via string diagrams, they are tree with sharing of subtrees, and with an 
an equivalence $\equiv$ on nodes that is closed under xxx. In plain words, if $a$ and $b$ are two constants such that
$a \equiv b$, then $f(a) \equiv f(b)$ for any unary operator $f$.

\cite[Section~4.2]{DetlefsNS05}
\cite{WillseyNWFTP21}
